The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-06 paper.tex
Add sentence about high bandwidth applications to main text
Direct comparison to EPICS/TANGO (#40)

The third hardware interface barrier: Some hardware interfaces are blocking or slow.
Experimental orchestration often means doing several things at once, \textit{e.g.} simultaneously moving several motors.
To accomplish this task performantly, monolithic orchestration software often necessitates separate threads for each component hardware interface, a fragile pattern in which small mistakes become both critical and elusive errors.
When writing orchestration software using \yaq{}, slow hardware interfaces are replaced by fast Avro-RPC.
In our experience, the \yaq{} interface is responsive enough to give good performace when orchestrating tens of motors using a singly-threaded client.
There is a longer discussion of timing and order-of-operations control details using \yaq{} in the Supplementary Material.

@@

>>>>

The third hardware interface barrier: Some hardware interfaces are blocking or slow.
Experimental orchestration often means doing several things at once, \textit{e.g.} simultaneously moving several motors.
To accomplish this task performantly, monolithic orchestration software often necessitates separate threads for each component hardware interface, a fragile pattern in which small mistakes become both critical and elusive errors.
When writing orchestration software using \yaq{}, slow hardware interfaces are replaced by fast Avro-RPC.
In our experience, the \yaq{} interface is responsive enough to give good performace when orchestrating tens of motors using a singly-threaded client.
There is a limit where using TCP becomes a bottleneck for large resonses, such as those from cameras or other high throughput sensors.
In our experience, this limit is approximately 1 megapixel.
For larger sensors, a pure \yaq{} approach may not be appropriate.
There is a longer discussion of timing and order-of-operations control details using \yaq{} in the Supplementary Material.

@@

We have designed \yaq{} to be easier to deploy and maintain when compared to EPICS and TANGO.
\yaq{} daemons are Python packages that can be installed on any platform using pip or conda.
There is no need for centralized management servers or databases when using \yaq{}.
The Avro RPC standard unambiguously describes the message signatures for any protocol, so users are always aware of the capabilities their hardware supports.
Traits enable interchangability where possible.
\yaq{} can easily be used alongside other experiment control software.
We provide tooling (\texttt{yaqd-control}) which makes it easy to configure, list, and manage daemons as background services on Windows, MacOS, or Linux (See SI for more details).
